\textbf{Case Studies II - Community Talks}

### 2013-04-09 ricardogarfe/final_report/001-apache-community-talk.tex
Update 001-apache-community-talk.tex

\par For a project, this is the previous step before become an Apache project. These projects are looking for create a hudge community and it's easier to become a contributor than in bigger projects from ASF.

@@

\begin{itemize}
	\item \textit{Contributor License Agreement} - to contribute with your commits to ASF.
	\item \textit{Account creation} - step by step using ASF standards.
	\item \textit{Responsibilities} - as a member of ASF, personal web space, community, ApacheCon.
\end{itemize} You can find an extense explanation in \href{http://www.apache.org/dev/new-committers-guide.html}{ASF new committers guide}.

>>>>

\par For a project, this is the previous step before become an Apache project. These projects are looking for create a huge community and it's easier to become a contributor than in bigger projects from ASF.

@@

\begin{itemize}
	\item \textit{Contributor License Agreement} - to contribute with your commits to ASF.
	\item \textit{Account creation} - step by step using ASF standards.
	\item \textit{Responsibilities} - as a member of ASF, personal web space, community, ApacheCon.
\end{itemize}  You can find an extensive explanation in ASF new committers at this link 
\url{http://www.apache.org/dev/new-committers-guide.html}.
% I change it because I think the reader can't know if there is a link . :)
